---
title: "iLipidome"
author: "WJ Lin"
date: "12/31/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
 <font size="4"> Here, we present iLipidome, a method for analyzing lipidomics data in the context of the lipid biosynthetic network, thus accounting for the interdependence of measured lipids. Currently, iLipidome only supports "two-group comparison", enabling users to identify essential altered lipid pathways and link lipidomic changes to their genetic origins. Further, it enhances statistical power and enables reliable clustering and lipid enrichment analysis. This tutorial describes a series of iLipidome functions to facilitate systems-level comparison of lipid profiles using a novel substructure-based approach. We hope it can provide researchers a deeper insight into complex lipidomic alterations across samples.</font> 




## Source function and load required data
 <font size="3"> Required function and data files can be found in the  "Required_function" and "Required_data" folder, respectively.</font>
 
```{r Source function and load required data}
file <- dirname(rstudioapi::getSourceEditorContext()$path)

# Source function
suppressWarnings(suppressPackageStartupMessages(source(file.path(file,'required_function.R'))))

# Load required data
load(file.path(file,'required_data.RData'))

```

## Upload lipidomics data

 <font size="3"> iLipidome only requires users to upload one processed lipid expression table (data.frame) where lipids are rows and samples are columns for analysis. Lipid names should be in the first column named as "feature", and sample names are in the first row (see example below).  At least two samples in each group are required to calculate statistics. Also, data processing or normalization methods, such as missing value imputation or log transformation, may be required based on data source to achieve better results before analysis.

Lipid names can be represented as:\
1. <span style="color:red">[LipidClass]</span>\_<span style="color:blue">[sum of FA chain length]</span>
<span style="font-weight:bold">:</span>
<span style="color:#FF8000">[sum of FA double bonds]</span>
<span style="font-weight:bold">;</span>
<span style="color:green">[sum of FA oxygens]</span>\
e.g., <span style="color:red">PC</span>\_<span style="color:blue">34</span><span style="font-weight:bold">:</span><span style="color:#FF8000">1</span><span style="font-weight:bold">;</span><span style="color:green">0</span> or 
<span style="color:red">TAG</span>\_<span style="color:blue">52</span><span style="font-weight:bold">:</span><span style="color:#FF8000">1</span><span style="font-weight:bold">;</span><span style="color:green">0</span> when the exact identity of FAs is unknown.\
2. <span style="color:red">[LipidClass]</span>\_<span style="color:blue">[FA1 chain length]</span>
<span style="font-weight:bold">:</span>
<span style="color:#FF8000">[FA1 double bonds]</span>
<span style="font-weight:bold">;</span>
<span style="color:green">[FA1 oxygens]</span>\_<span style="color:blue">[FA2 chain length]</span>
<span style="font-weight:bold">:</span>
<span style="color:#FF8000">[FA2 double bonds]</span>
<span style="font-weight:bold">;</span>
<span style="color:green">[FA2 oxygens]</span>...\
e.g., <span style="color:red">PC</span>\_<span style="color:blue">16</span><span style="font-weight:bold">:</span><span style="color:#FF8000">0</span><span style="font-weight:bold">;</span><span style="color:green">0</span>\_<span style="color:blue">18</span><span style="font-weight:bold">:</span><span style="color:#FF8000">1</span><span style="font-weight:bold">;</span><span style="color:green">0</span> or 
<span style="color:red">TAG</span>\_<span style="color:blue">16</span><span style="font-weight:bold">:</span><span style="color:#FF8000">0</span><span style="font-weight:bold">;</span><span style="color:green">0</span>\_<span style="color:blue">18</span><span style="font-weight:bold">:</span><span style="color:#FF8000">0</span><span style="font-weight:bold">;</span><span style="color:green">0</span>\_<span style="color:blue">18</span><span style="font-weight:bold">:</span><span style="color:#FF8000">1</span><span style="font-weight:bold">;</span><span style="color:green">0</span> when the exact identity of FAs is known.

Supported lipid classes, abbreviations, and corresponding FA numbers can be found in the "supported_lipid_class.csv" file. Note that lipid classes with same FA numbers (e.g., PC, PE) in same pathways (e.g., Glycerophospholipid) should have consistent lipid naming format (e.g., PC_36:0;0 and PE_34:0;0 or PC_18:0;0_18:0;0 and PE_16:0;0_18:0;0). Further, dihydrosphingolipids (dh-) specify the sphingolipids with sphingoid bases of 18:0:2 instead of 18:1:2.</font>


```{r Upload lipidomics data and process format}

#Expression table of example lipidomics dataset
exp <- read.csv(file.path(file, 'exp.csv'))

head(exp)

```

## Process data for iLipidome inputs

 <font size="3"> "build_char_table" transforms lipid expression table ("exp") into two iLipidome inputs: selected lipid expression table  ("exp_sel") and selected lipid characteristics table ("char_sel"). Note that it only considers the lipid classes recorded in the "network_node" table.</font>

```{r Upload lipidomics data and process format2}

#raw_data: A data.frame where rows are lipid species and columns are samples. Lipid names should be provided in the first column. Lipid values should be numeric.
#network_node: A data.frame recording iLipidome-supported lipid classes and related information.

exp_sel <- build_char_table(raw_data=exp, network_node = network_node)[[1]]

#selected lipid expression table
head(exp_sel)

char_sel <- build_char_table(exp, network_node = network_node)[[2]]

#selected lipid characteristics table
head(char_sel)

```

## Analysis for unprocessed data
 <font size="3"> "unprocessed_data_test" uses the output of "build_char_table" to perform differential expression for three types of data: (1) lipid species, (2) fatty acids, and (3) lipid classes.</font>

```{r Analysis for unprocessed data}

#exp_data: Lipid expression table. Output of "build_char_table".
#char_table: Lipid characteristics table. Output of "build_char_table".
#method: A character string indicating which statistical method to be. Currently, iLipidome supports two-sample t-tests ("t.test"), Wilcoxon tests ("wilcox.test"), or moderated t-tests ("mod.t.test").
#significant: "p_value" or "adj_p_value" can be used for selecting significant lipid features.
#ctrl_group: An integer vector specifying samples in the control group in lipid expression table. Note that the first column containing lipid names is not counted.
#exp_group: An integer vector specifying samples in the experimental group in lipid expression table. Note that the first column containing lipid names is not counted.

no_sub_t <- unprocessed_data_test(exp_data = exp_sel,
                                  char_table = char_sel,
                                  method = 't.test',
                                  significant='adj_p_value',
                                  ctrl_group = 1:7, exp_group = 8:13)

#Expression tables for lipid species, fatty acids, and lipid classes
no_sub_t[[1]] %>% head()

#Statistical result table for lipid species, fatty acids, and lipid classes
no_sub_t[[2]] %>% head()

```

## 1. FA substructure analysis
 <font size="3"> Here, we provide a step-by-step process to perform FA substructure analysis using the data above and a series of functions.</font>

### 1-1. FA biosynthetic network transformation
 <font size="2"> Firstly, the reference FA biosynthetic network is trimmed by users' data.</font>
 
```{r FA substructure analysis 1}

#FA_network: A data.frame describing the reference FA biosynthetic network in iLipdiome.
#unprocessed_data_result: Differential expression for unprocessed lipidomics data. Output of "unprocessed_data_test".

FA_network_new <- build_FA_net(FA_network = FA_network,
                           unprocessed_data_result = no_sub_t)

#Trimmed FA biosynthetic network
FA_network_new %>% head()

```

### 1-2. Decompose FAs into FA substructures
 <font size="2"> "FA_sub_transform" decomposes FAs into FA substructures based on the FA biosynthetic network.</font>
 
```{r FA substructure analysis 2}

#FA_network: Trimmed FA biosynthetic network. Output of "build_FA_net".
#unprocessed_data_result: Differential expression for unprocessed lipidomics data. Output of "unprocessed_data_test".
#unmapped_FA: An character vector allowing users to decide which FAs should be ignored since some FAs can be mapped to more than one node in FA network (e.g., 20:4;0 for w6-20:4;0 and w3-20:4;0). 

#18:2 and 20:4 are majorly omega-6 FAs, so we only kept omega-6 forms of them.

FA_substructure <- FA_sub_transform(FA_network = FA_network_new,
                                    unprocessed_data_result = no_sub_t,
                                    unmapped_FA = c('w9-18:2;0','w3-20:4;0'))

#FA substructure table
FA_substructure %>% head()



```

### 1-3. Extract FA substructures using fold changes
 <font size="2"> "FA_sub_extract" maps FA substructures in each pathway with fold changes from the "unprocessed_data_test" result and extracts them through a backpropagated process. Specifically, the checking process starts from the last substructure (target FA) and would not stop until it meets a substructure with an opposite fold change along the biosynthetic route. One exception is the endogenous biosynthesis pathway for FAs in the upstream of palmitate (e.g., 14:0 or 12:0). Since they are synthesized as a group (2:0 to 16:0), we do not check their fold change and keep all substructures.</font>

```{r FA substructure analysis 3}

#char_table: Lipid characteristics table. Output of "build_char_table".
#FA_substructure: FA substructure table. Output of "FA_sub_transform".
#unprocessed_data_result: Differential expression for unprocessed lipidomics data. Output of "unprocessed_data_test".
#exact_FA: "yes" or "no" to decide if the exact FA identity (e.g., w3 or w6) is known or not.
#exo_lipid: An character vector specifying exogenous lipid addition. The exogenous lipids and their adjacent nodes in FA network will not be decomposed.

FA_sub_stop <- FA_sub_extract(char_table = char_sel,
                              FA_substructure = FA_substructure,
                              unprocessed_data_result = no_sub_t,
                              exact_FA='no', exo_lipid='w3-22:6;0')

#lipid species
FA_sub_stop[[1]] %>% head()

#Extracted FA substructures for lipid species
FA_sub_stop[[2]] %>% head()


```

### 1-4. Transform FA exp into substructure exp

 <font size="2"> The function converts expression of FAs to expression of FA substructures.</font>
 
```{r FA substructure analysis 4}

#exp_data: Lipid expression table. Output of "build_char_table".
#sub_data: Extracted substructure data. Output of "FA_sub_extract".
#sub_type: "FA", "Class", or "Species" to indicate which type of substructure.

FA_sub_exp <- lipid_sub_matrix(exp_data = exp_sel, sub_data = FA_sub_stop,
                               sub_type = 'FA')

#FA substructure matrix encoding the frequency of each substructure 
FA_sub_exp[[1]][1:5, 1:5]

#Lipid profile
FA_sub_exp[[2]]%>% head()

#FA substructure profile
FA_sub_exp[[3]] %>% head()


```

### 1-5. Differential expression analysis for FA substructures

```{r FA substructure analysis 5}

#data: FA substructure profile. Output of "lipid_sub_matrix".
#ctrl: An integer vector specifying samples in the control group in lipid expression table. Note that the first column containing lipid names is not counted.
#exp: An integer vector specifying samples in the experimental group in lipid expression table. Note that the first column containing lipid names is not counted.
#method: A character string indicating which statistical method to be. Currently, iLipidome supports two-sample t-tests ("t.test"), Wilcoxon tests ("wilcox.test"), or moderated t-tests ("mod.t.test").
#significant: "p_value" or "adj_p_value" can be used for selecting significant lipid features.

FA_sub_exp_t <- t_test(data = FA_sub_exp[[3]], ctrl = 1:7, exp = 8:13,
                       method = 't.test', significant = 'adj_p_value')

#Statistical result table for FA substructures
FA_sub_exp_t %>% head()

```

### 1-6. Essential pathway analysis for FA substructures

 <font size="2"> "path_scoring" use FA substructures to score pathways in FA biosynthetic network.</font>

```{r FA substructure analysis 6}

#network: Trimmed FA biosynthetic network. Output of "build_FA_net".
#sub_t: Statistical result table for substructures. Output of "t_test".
#calibrate: "True" or "False" to calibrate pathway scores or not.
#data_type: "FA", "Class", or "Species" to indicate which type of substructure.

set.seed(1)
path_score_FA <- path_scoring(network = FA_network_new, sub_t = FA_sub_exp_t, 
                              calibrate = T, data_type = 'FA')

#Pathway scoring result table
path_score_FA %>% head()


```

### 1-7. Essential edges (reactions) analysis for FA substructures

 <font size="2"> "reaction_scoring" evaluates each reaction in FA biosynthetic network using FA substructures.</font>

```{r FA substructure analysis 7}

#network: Trimmed FA biosynthetic network. Output of "build_FA_net".
#sub_exp: Substructure profile. Output of "lipid_sub_matrix".
#sub_t: Statistical result table for substructures. Output of "t_test".
#ctrl: An integer vector specifying samples in the control group in lipid expression table. Note that the first column containing lipid names is not counted.
#exp: An integer vector specifying samples in the experimental group in lipid expression table. Note that the first column containing lipid names is not counted.
#Species: "human", "mouse", or "rat" can be used to label species-specific genes for lipid reactions.

reaction_score_FA <- reaction_scoring(network = FA_network_new, 
                                      sub_exp = FA_sub_exp[[3]],
                                      sub_t = FA_sub_exp_t, 
                                      ctrl = 1:7, exp = 8:13, 
                                      Species = 'rat')

#Reaction scoring result table
reaction_score_FA %>% head()


```

### 1-8. FA biosynthetic network construction

 <font size="2"> Build the FA biosynthetic network using FA substructures, pathway and reaction scoring results.</font>

```{r FA substructure analysis 8}

#network_data: Trimmed FA biosynthetic network. Output of "build_FA_net".
#DE_data: Statistical result table for substructures. Output of "t_test".
#if_species: "True" or "False" to indicate data type is lipid species or the others (FA or class).
#significant: "p_value" or "adj_p_value" can be used for selecting significant lipid features.
#path_scoring_result: Pathway scoring result table. Output of "path_scoring".
#reaction_scoring_result: Reaction scoring result table. Output of "reaction_scoring".
#top_n: 1 to 5 to label top N pathways and reactions.
#path_type: "active", "suppressed", or "both" is used to select specific types of top N pathways and reactions.

FA_network_data <- draw_network(network_data = FA_network_new,
                                DE_data = FA_sub_exp_t,
                                if_species = F, significant = 'adj_p_value',
                                path_scoring_result = path_score_FA,
                                reaction_scoring_result = reaction_score_FA,
                                top_n = 5, path_type = 'both')

#FA biosynthetic network node
FA_network_data[[1]] %>% head()

#FA biosynthetic network edge
FA_network_data[[2]] %>% head()

#FA biosynthetic network
visNetwork(FA_network_data[[1]],FA_network_data[[2]]) %>% 
  visIgraphLayout(layout = "layout_with_sugiyama", type='square',
                  physics = F, smooth = TRUE, randomSeed =5) 


```


## 2. Lipid species substructure analysis

 <font size="3"> A similar approach can be used to analyze lipid species substructures.</font>

### 2-1. Decompose lipids into species substructures

 <font size="2"> "species_sub_transform" decomposes lipids into species substructures based on the lipid biosynthetic network.</font>
 
```{r Lipid species substructure analysis 1}

#We excluded ether lipids since we cannot differentiate Alkyl (O-) or Alkenyl- (P-) linked ether lipids

char_wo_EL <- char_sel[!str_detect(char_sel$feature, 'O-'),]
exp_wo_EL <- exp_sel[!str_detect(exp_sel$feature, 'O-'),]

#char: Lipid characteristics table. Output of Output of "build_char_table".
#lipid_substructure: A data.frame recording lipid class substructures computed from the reference lipid biosynthetic network in iLipdiome.
#network_node: A data.frame recording iLipidome-supported lipid classes and related information.

species_substructure <- species_sub_transform(char = char_wo_EL,
                                              lipid_substructure = lipid_substructure,
                                              network_node = network_node)


#Lipid species substructure table
species_substructure %>% head()

```

### 2-2. Extract species substructures using fold changes
 <font size="2"> "species_sub_extract" maps species substructures in each pathway with fold changes from the "unprocessed_data_test" result and extracts them through a backpropagated process. Specifically, the checking process starts from the last substructure (target species) and would not stop until it meets a substructure with an opposite fold change along the biosynthetic route.</font>

```{r Lipid species substructure analysis 2}

#lipid_substructure: Lipid species substructure table. Output of "species_sub_transform".
#unprocessed_data_result: Differential expression for unprocessed lipidomics data. Output of "unprocessed_data_test".
#type: "species" or "class" to indicate which type of substructure.
#pct_limit: A threshold of non-NA percent (0~1) in one biosynthetic route can be set to control decompostion process and reduce artifacts. If the proportion of non-missing substructures exceeds the threshold in one biosynthetic route, the target lipid species will not be decomposed to substructures.
#exo_lipid: An character vector specifying exogenous lipid addition. The exogenous lipids and their adjacent nodes in FA network will not be decomposed.


species_sub_stop <- species_sub_extract(lipid_substructure = species_substructure,
                                        unprocessed_data_result =  no_sub_t,
                                        type = 'species', pct_limit = 0.3,
                                        exo_lipid=NULL)

#Lipid species
species_sub_stop[[1]] %>% head()

#Extracted species substructures for lipid species
species_sub_stop[[2]] %>% head()


```

### 2-3. Transform lipid exp into substructure exp

 <font size="2"> The function converts expression of lipid species to expression of species substructures.</font>
 
```{r Lipid species substructure analysis 3}

#exp_data: Lipid expression table.
#sub_data: Extracted substructure data. Output of "species_sub_extract".

species_sub_exp <- lipid_sub_matrix(exp_data = exp_wo_EL, 
                                    sub_data = species_sub_stop,
                                    sub_type = 'Species')


#Species substructure matrix encoding the frequency of each substructure 
species_sub_exp[[1]][1:5, 1:5]

#Lipid profile
species_sub_exp[[2]] %>% head()

#Species substructure profile
species_sub_exp[[3]] %>% head()


```

### 2-4. Differential expression analysis for species substructures

```{r Lipid species substructure analysis 4}

species_sub_exp_t <- t_test(data = species_sub_exp[[3]], ctrl = 1:7, exp = 8:13,
                            method = 't.test', significant = 'adj_p_value')


#Statistical result table for species substructures
species_sub_exp_t %>% head()

```

### 2-5. Lipid species biosynthetic network transformation

 <font size="2"> "build_species_net" uses species substructures to contruct lipid biosynthetic network.</font>

```{r Lipid species substructure analysis 5}

#species_substructure: Output of "species_sub_transform".

species_network <- build_species_net(species_substructure = species_substructure)

#Lipid species biosynthetic network
species_network %>% head()


```

### 2-6. Essential pathway analysis for species substructures

 <font size="2"> "path_scoring" use species substructures to score pathways in lipid species biosynthetic network.</font>

```{r Lipid species substructure analysis 6}

#network: Lipid species biosynthetic network. Output of "build_species_net".

set.seed(1)
path_score_species <-  path_scoring(network = species_network,
                                    sub_t = species_sub_exp_t,
                                    calibrate = T, data_type = 'Species')


#Pathway scoring result table
path_score_species %>% head()


```

### 2-7. Essential edges (reactions) analysis for species substructures

 <font size="2"> "add_rev_rection" completes all reversible reactions in lipid species biosynthetic network, where "reaction_scoring" evaluates each reaction using species substructures.</font>

```{r Lipid species substructure analysis 7}

#network_edge: A data.frame recording edge information of the reference lipid biosynthetic network in iLipdiome.
#species_net: Lipid species biosynthetic network. Output of "build_species_net".

species_net_w_rev <- add_rev_rection(network_edge = network_edge,
                                     species_net = species_network)

#Lipid species biosynthetic network with complete reversible reactions
species_net_w_rev %>% head()


#network: Lipid species biosynthetic network with complete reversible reactions. Output of "add_rev_rection".

reaction_score_species <- reaction_scoring(network = species_net_w_rev,
                                           sub_exp = species_sub_exp[[3]],
                                           sub_t = species_sub_exp_t,
                                           ctrl=1:7, exp=8:13,
                                           Species = 'rat')

#Reaction scoring result table
reaction_score_species %>% head()


```

### 2-8. Lipid species biosynthetic network construction

 <font size="2"> Build the lipid species biosynthetic network using species substructures, pathway and reaction scoring results.</font>

```{r Lipid species substructure analysis 8}

#network_data: Lipid species biosynthetic network with complete reversible reactions. Output of "add_rev_rection".

species_network_data <- draw_network(network_data = species_net_w_rev,
                                     DE_data = species_sub_exp_t,
                                     if_species = T,significant = 'adj_p_value',
                                     path_scoring_result = path_score_species,
                                     reaction_scoring_result = reaction_score_species,
                                     top_n = 3, path_type = 'both')



#Lipid species biosynthetic network node
species_network_data[[1]] %>% head()

#Lipid species biosynthetic network edge
species_network_data[[2]] %>% head()

#Lipid species biosynthetic network
visNetwork(species_network_data[[1]], species_network_data[[2]])


```


## 3. Lipid class substructure analysis

<font size="3"> A similar approach can be used to analyze lipid class substructures.</font>

### 3-1. Extract class substructures using fold changes

```{r Lipid class substructure analysis 1}

#lipid_substructure: A data.frame recording lipid class substructures computed from the reference lipid biosynthetic network in iLipdiome.

class_sub_stop <- species_sub_extract(lipid_substructure =lipid_substructure,
                                      unprocessed_data_result = no_sub_t,
                                      type = 'class', pct_limit = 0.01,
                                      exo_lipid=NULL)


#Lipid classes
class_sub_stop[[1]] %>% head()

#Extracted class substructures for lipid classes
class_sub_stop[[2]] %>% head()


```

### 3-2. Transform lipid class exp into substructure exp

 <font size="2"> The function converts expression of lipid classes to expression of class substructures.</font>
 
```{r Lipid class substructure analysis 2}

#Lipid class expression table.
class_exp <- no_sub_t[[1]] %>% filter(type=='class') %>% 
  dplyr::select(-type)

#exp_data: Lipid class expression table.
#sub_data: Extracted substructure data. Output of "species_sub_extract".

class_sub_exp <- lipid_sub_matrix(exp_data = class_exp, 
                                    sub_data = class_sub_stop,
                                    sub_type = 'Class')


#Class substructure matrix encoding the frequency of each substructure 
class_sub_exp[[1]][1:5, 1:5]

#Lipid class profile
class_sub_exp[[2]] %>% head()

#Class substructure profile
class_sub_exp[[1]] %>% head()


```

### 3-3. Differential expression analysis for lipid class substructures

```{r Lipid class substructure analysis 3}

class_sub_exp_t <- t_test(data = class_sub_exp[[3]], ctrl = 1:7, exp = 8:13,
                          method = 't.test', significant = 'adj_p_value')

#Statistical result table for class substructures
class_sub_exp_t %>% head()

```

### 3-4. Lipid class biosynthetic network transformation

 <font size="2"> The reference lipid biosynthetic network in iLipdiome is trimmed by class substructures to build lipid class network.</font>

```{r Lipid class substructure analysis 4}

class_network <- network_edge[c('S1','P1')] %>% 
  filter(S1 %in% class_sub_exp_t$lipid, P1 %in% class_sub_exp_t$lipid)

#Lipid class biosynthetic network
class_network %>% head()


```

### 3-5. Essential pathway analysis for species substructures

 <font size="2"> "path_scoring" use class substructures to score pathways in lipid class biosynthetic network.</font>

```{r Lipid class substructure analysis 5}

#network: Lipid class biosynthetic network.

set.seed(1)
path_score_class <-  path_scoring(network = class_network,
                                    sub_t = class_sub_exp_t,
                                    calibrate = T, data_type = 'Class')


#Pathway scoring result table
path_score_class %>% head()


```

### 3-6. Essential edges (reactions) analysis for species substructures

 <font size="2"> “reaction_scoring” evaluates each reaction in lipid class biosynthetic network using class substructures.</font>

```{r Lipid class substructure analysis 6}

#network: Lipid class biosynthetic network.

reaction_score_class <- reaction_scoring(network = class_network,
                                         sub_exp = class_sub_exp[[3]],
                                         sub_t = class_sub_exp_t,
                                         ctrl=1:7, exp=8:13,
                                         Species = 'rat')



#Reaction scoring result table
reaction_score_class %>% head()


```

### 3-7. Lipid class biosynthetic network construction

 <font size="2"> Build the lipid class biosynthetic network using class substructures, pathway and reaction scoring results.</font>

```{r Lipid class substructure analysis 7}

#network_data: Lipid class biosynthetic network.

class_network_data <- draw_network(network_data = class_network,
                                     DE_data = class_sub_exp_t,
                                     if_species = F,significant = 'adj_p_value',
                                     path_scoring_result = path_score_class,
                                     reaction_scoring_result = reaction_score_class,
                                     top_n = 3, path_type = 'both')


#Lipid class biosynthetic network node
class_network_data[[1]] %>% head()

#Lipid class biosynthetic network edge
class_network_data[[2]] %>% head()

#Lipid class biosynthetic network
visNetwork(class_network_data[[1]], class_network_data[[2]])


```